\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-11 paper/main.tex
fill in references to lines in Fig 2

\subsubsection{The onion comment}\label{subsec:onion}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it. Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippets})} (see Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_ for examples).
%For examples of \texttt{smuggle} statements and accompanying onion comments, see Figure \ref{fig:snippets}.
%Figure \ref{fig:snippets} provides a number of examples of \texttt{smuggle} statements accompanied by

Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_). However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}. If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints. If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided. If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead. Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_).

@@

\texttt{davos} processes onion comments internally before forwarding arguments to the installer program. In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_). For example, \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will disable \texttt{davos}'s input prompts in addition to \texttt{pip}'s; and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to \texttt{sys.path}, if necessary, so the package can be imported.

>>>>

\subsubsection{The onion comment}\label{subsec:onion}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it. Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippets})} (see Fig.~\ref{fig:snippets}, lines 3--10 for examples).
%For examples of \texttt{smuggle} statements and accompanying onion comments, see Figure \ref{fig:snippets}.
%Figure \ref{fig:snippets} provides a number of examples of \texttt{smuggle} statements accompanied by

Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippets}, lines 12--13). However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}. If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippets}, lines 15--19), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints. If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided. If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead. Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippets}, lines 21--22).

@@

\texttt{davos} processes onion comments internally before forwarding arguments to the installer program. In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippets}, lines 24--28). For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flag will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will disable \texttt{davos}'s input prompts in addition to the installer program's; and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported.
